A new tidy data structure to support exploration and modeling of temporal data

### 2019-08-30 tsibble.Rmd
revert to the tsibble principles

The choice of tidy representation of temporal data arises from a data- and model-oriented perspective, which can accommodate all of the operations that are to be performed on the data in time-based contexts. Figure \@ref(fig:tsibble-fit) marks where this new abstraction is placed in the tidy model, which is referred to as a "tsibble". We adapt the "tidy data" principles in tsibble with the following principles:

1. The Index is a variable with inherent ordering from past to present.
2. The Key is a set of variables that define observational units over time
3. Each observation should be uniquely identified by Index and Key.
4. When each observational unit is measured at a common interval, the data set is described as "regularly spaced".

@@

The new tsibble structure bridges the gap between raw data and the rigorous state of temporal data analysis. The proposed contextual semantics is the new add-on to tidy data in order to support more intuitive time-related manipulations and enlighten new perspectives for time series and panel model inputs. The Index, Key and time interval are the three pillars to this new semantically structured temporal data. Each is now described in more detail.

@@

A common practice with energy data analysis is load forecasting, because providers need to know they have capacity to supply electricity. To illustrate the pipeline including modeling, we model demand for December 2013, with the usage forecast for the last day (48 steps ahead because the data is half-hourly). The energy data for the last day is not used for modeling. ARIMA models with and without a temperature covariate are fitted using automatic order selection [@autoarima]. The logarithmic transformation is applied to the average demand to ensure positive forecasts. Figure \@ref(fig:elec-forecast) plots one-day forecasts from both models against the actual demand, for the last two-week window. The ARIMA model which includes the average temperature covariate gives a better fit than the one without, although both tend to underestimate the night demand. The forecasting performance is reported in Table \@ref(tab:elec-accuracy), consistent with the findings in Figure \@ref(fig:elec-forecast).

>>>>

The choice of tidy representation of temporal data arises from a data- and model-oriented perspective, which can accommodate all of the operations that are to be performed on the data in time-based contexts. Figure \@ref(fig:tsibble-fit) marks where this new abstraction is placed in the tidy model, which is referred to as a "tsibble". The "tidy data" principles are adapted in tsibble with the following rules:

1. Index is a variable with inherent ordering from past to present.
2. Key is a set of variables that define observational units over time
3. Each observation should be uniquely identified by index and key.
4. Each observational unit should be measured at a common interval, if regularly spaced.

@@

The new tsibble structure bridges the gap between raw data and the rigorous state of temporal data analysis. The proposed contextual semantics is the new add-on to tidy data in order to support more intuitive time-related manipulations and enlighten new perspectives for time series and panel model inputs. Index, key and time interval form the three pillars to this new semantically structured temporal data. Each is now described in more detail.

@@

A common practice with energy data analysis is load forecasting, because providers need to know they have capacity to supply electricity. To illustrate the pipeline including modeling, here demand is modeled for December 2013, with the usage forecast for the last day (48 steps ahead because the data is half-hourly). The energy data for the last day is not used for modeling. ARIMA models with and without a temperature covariate are fitted using automatic order selection [@autoarima]. The logarithmic transformation is applied to the average demand to ensure positive forecasts. Figure \@ref(fig:elec-forecast) plots one-day forecasts from both models against the actual demand, for the last two-week window. The ARIMA model which includes the average temperature covariate gives a better fit than the one without, although both tend to underestimate the night demand. The forecasting performance is reported in Table \@ref(tab:elec-accuracy), consistent with the findings in Figure \@ref(fig:elec-forecast).
